### 2020-06-28 Report/aws_325ghz_study.tex
A few changes after a reading of the newest sections.

\section*{Summary}
%
The main objective of this study is to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
mission. In this study, we investigate the possibility to use the 325\,GHz
channels instead. The cloud impact of high altitude cirrus clouds is
considerably higher in 325\,GHz and this makes it possible to estimate the weak
cloud impact at 183 GHz with relatively good accuracy.

@@

Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are
considered. For $T_r$ = 1200\,K, the DoF from all four options is around 8,
however, increase in receiver noise leads to a loss in the DoF.
Table~\ref{tab:DoF:clear} and Table~\ref{tab:DoF:cloudy} show the DoF for
clear-sky and cloudy cases respectively. For clear-sky situations, the DoFs are
about 77. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
have only 5 DoF for option three-a and 4.8 for both option three-b/c and 4.9
for option four. On the other hand, the presence of clouds increases the DoF
significantly. For all three options, we have DoF close to 9. Increase in noise
has a lower effect on the DoF for cloudy cases.

@@

\subsection{Impact of extending the IF range}
%
As a basic investigation of the impact of changing the width of the IF range, a
version of the four channel option was considered, denoted as four-b. It was
modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
extension, only the edge channels were changed. That is, the revised AWS-41 and
have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
are found in Table~\ref{tab:DoF:4b}.

@@

That is, a broader IF range should give slightly better performance. If a
broader IF range is feasible, the position and width of all channels should be
revised, bit this is out of the scope of this study and anyhow hardly motivated
before it is known more exactly to what extent the IF range can be extended.

@@

\subsection{Technical recommendations}
%
The cloud correction and filtering results gave no clear indications on the
requirements of the channels, and as a complement also the measurements' degree
of freedom (DoF) were assessed. The later analysis gave a bit clearer
indications and the discussion in this section is mainly based on the DoF results.

@@

\subsubsection{Channel specifications}
%
We formed three first 325\,GHz channel options. All three options were
considered only in the QRNN part as it is difficult to maintain the full
information of all channels in a simple regression based scheme. None of the
three options gave consistently best results, and it is not possible to give a
clear recommendation. For this reason we did not see any value in testing
further options in this part.

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. Option three-a risks to be affected by interference of the downlink
and in options three-b and c there is a high ratio between bandwidth and centre
IF of AWS-42. This aspect also makes it hard to extend options three-b and c if
it would turn out that the IF range can be extended. A brief analysis showed
that a broader IF range gives some increase in DoF, that potentially could
improve the merit of the four channel option.

We don't see how these results can be boiled down to threshold, target and
breakthrough requirements. Option 3c came out best here, but the full
optimisation of the options was made and a modified or extended four channel
version could reach the same performance. In any case, the differences between
the options are small and it seems reasonable to allow that  the technically
most simple option is selected (that in fact can be the four channel one).
When this selection is done and the technical constraints are better known (IF
range available, needed frequent gaps between channels), an iteration of DoF
analysis should be made to see if some ``optimisation'' of the channel
specifications can be achieved.

Further, the simulations have assumed rectangular shaped response functions.
This was done for simplicity and shall in no way be taken as an indication on
that this shape is required. We have left some frequency gaps between the
channels to simplify the technical implementation, i.e.\ to decrease the demand
on very sharp transitions from high to low response.

@@

\section{Conclusion}
%
This study compares the options of having a channel at 229\,GHz or having some
around 325\,GHz from a single perspective, cloud filtering/correction of
183\,GHz data. There could be other important reasons to consider for the
selection.

>>>>

\section*{Summary}
%
The main objective of this study is to demonstrate that channels around
325\,GHz can provide a basis for cloud filtering/correction of data measured
around 183\,GHz. Previously, it was suggested that a channel at 229\,GHz to be
used for cloud filtering. The 229\,GHz channel forms a part of the MicroWave
Sounder (MWS) and will be used for cloud filtering of 183\,GHz inside that
mission. In this study, we investigate the possibility to use some 325\,GHz
channels instead.

@@

Table~\ref{tab:DoF:all} shows the DoF with 325\,GHz when all cases are
considered. For $T_r$ = 1200\,K, the DoF from all four options is around 8,
however, increase in receiver noise leads to a loss in the DoF.
Tables~\ref{tab:DoF:clear} and \ref{tab:DoF:cloudy} show the DoF for
clear-sky and cloudy cases respectively. For clear-sky situations, the DoFs are
about 7. With increase in $T_r$, the DoF are degraded. For $T_r$ = 2400\,K, we
have only 5 DoF for option three-a and 4.8 for both option three-b/c and 4.9
for option four. On the other hand, the presence of clouds increases the DoF
significantly. For all three options, we have DoF close to 9. Increase in noise
has a lower effect on the DoF for cloudy cases.

@@

\subsection{Impact of extending the IF range}
%
As a basic investigation of the impact of changing the width of the IF range, a
version of the four channel option was considered, denoted as four-b. It was
modified to cover 0.7 to 9.0 GHz (instead of 0.7 to 8.0 GHz). To focus on the
extension, only the edge channels were changed. That is, the revised AWS-41 and AWS-43
have bandwidth of 3.8 and 0.9\,GHz, respectively. The DoFs obtained for four-b
are found in Table~\ref{tab:DoF:4b}.

@@

That is, a broader IF range should give slightly better performance. If a
broader IF range is feasible, the position and width of all channels should be
revised, but this is out of the scope of this study and anyhow hardly motivated
before it is known more exactly to what extent the IF range can be extended.

@@

\subsection{Technical recommendations}
%
The cloud correction and filtering results gave no clear indications on the
requirements of the channels, and as a complement also the measurements' degree
of freedom (DoF) was assessed. The later analysis gave a bit clearer
indications and the discussion in this section is mainly based on the DoF results.

@@

\subsubsection{Channel specifications}
%
We formed three 325\,GHz channel options. All three options were
considered first in the QRNN part as it is difficult to maintain the full
information of all channels in a simple regression based scheme. None of the
three options gave consistently best results, and it is not possible to give a
clear recommendation. For this reason we did not see any value in testing
further options in this part.

Some further channel options were included on the DoF analysis. Staying inside
0.8\,-\,8.0\,GHz in terms of IF, the option three-c was found to have the
highest overall DoF, but the differences to three-b and four are relatively
small. However, it could be challenging to implement any of the three channel
options. Option three-a risks to be affected by interference of the downlink
and in options three-b and c there is a high ratio between bandwidth and centre
IF of AWS-42. The later aspect also makes it hard to extend options three-b and c if
it would turn out that the IF range can be extended. A brief analysis showed
that a broader IF range gives some increase in DoF, that potentially could
improve the merit of the four channel option.

We don't see how these results can be boiled down to threshold, target and
breakthrough requirements. Option 3c came out best here, but no full
optimisation of the options was made, and a modified or extended four channel
version could possibly reach the same performance. In any case, the differences
between the options are small and it seems reasonable to allow that the
technically most simple option is selected (that in fact can be the four
channel one). When this selection is done and the technical constraints are
better known (IF range available, needed frequent gaps between channels etc.), an
iteration of DoF analysis should be made to see if some ``optimisation'' of the
channel specifications can be achieved.

Further, the simulations have assumed rectangular shaped response functions.
This was done for simplicity and shall in no way be taken as an indication on
that this shape is required. We have left some frequency gaps between the
channels to simplify the technical implementation, i.e.\ to decrease the demand
on very sharp transitions from high to low response, but if gaps of 200\,MHz
actually are required or if some overlap of the responses can be tolerated is
not known to us.

@@

\newpage
\section{Conclusion}
%
This study compares the options of having a channel at 229\,GHz or having some
around 325\,GHz from a single perspective, cloud filtering/correction of
183\,GHz data. There could be other important reasons to consider for the
selection.
